---
title: "fireSense_dataPrepFit"
author: 
  - Ian Eddy
  - Alex Chubaty
date: "September 2020; updated February 2022"
output:
  html_document:
    keep_md: yes
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE, results = "hold", message = FALSE)
```

# Overview

Prepare data required by `fireSense_IginitionFit`, `fireSense_EscapeFit`, and `fireSense_SpreadFit`.

# Parameters

Provide a summary of user-visible parameters.

```{r moduleParams, echo = FALSE, eval = TRUE}
df_params <- SpaDES.core::moduleParams("fireSense_dataPrepFit", "..")
knitr::kable(df_params)
```

# Events

Describe what happens for each event type.

## Plotting

Write what is plotted.

## Saving

Write what is saved.

# Data dependencies

## Input data

How to obtain input data, and a description of the data required by the module.
If `sourceURL` is specified, `downloadData("fireSense_dataPrepFit", "..")` may be sufficient.

```{r moduleInputs, echo = FALSE, eval = TRUE}
df_inputs <- SpaDES.core::moduleInputs("fireSense_dataPrepFit", "..")
knitr::kable(df_inputs)
```

## Output data

Description of the module outputs.

```{r moduleOutputs, echo = FALSE, eval = TRUE}
df_outputs <- SpaDES.core::moduleOutputs("fireSense_dataPrepFit", "..")
knitr::kable(df_outputs)
```

# Links to other modules

Outputs used by `fireSense_IginitionFit`, `fireSense_EscapeFit`, and `fireSense_SpreadFit`.
